Title

### 2019-05-22 4_method.tex
lil
rewrite gMAT section

\subsection{Method Overview}
\begin{enumerate}
\item compute medial axis transform (MAT)
\item find places `of high curvature' in the medial axis and mark those regions
\item transform the $R$ distance measures in the marked regions to enable fitting an integer multiple beads.
		This transformation uses transition regions to smoothly transition from $n$ into $n+1$ insets.
\item introduce extra `joints' on the medial axis in order to discretize the transformed distance measure
\item connect these new joints to the outline with new `bones' (In the standard MAT manner)
\item (optional) transform $R$ fields along all bones, while keeping the endpoint bead measures fixed. (Deviate from evenly distributed linear space in order to have outer outlines closer to the nominal bead width and only change the innermost couple of toolpaths.)
\item define locations everywhere on the bones of the medial axis at integer MAT distances
\item connect all locations with odd distance measure to form the inset toolpaths
\item connect all even locations to form the extent of the toolpaths, which defines the variable width of the segments.
\end{enumerate}

@@

Based on the straight skeleton naming, I would like to introduce a new consistent terminology:
\begin{itemize}
\item marked medial axis segment: vertebra
\item marked medial axis: spine
\item non-marked medial axis segment: arm
\item any medial axis segment: bone
\item bone introduced to the medial axis: rib
\item medial axis vert: joint
\item introduced medial axis vert: ligament?
\item location of an insets along a bone: tick? locus?
\end{itemize}

@@

The medial axis is commonly defined either as the set of points with more than one closest point on the boundary or as the set of quench sites of a fire started at the outline polygon growing inward.
A novel way of conceptualizing the medial axis is as an efficient data structure to store a distance field.
The medial axis is the set of all points where the derivative of the distance field is discontinuous.

By introducing extra bones to the MAT, we can approximate insets from the medial axis by connecting points on the segments of the MAT using linear segments.

We introduce the Grounded Medial Axis Transform.
We dscretize the segments of the MAT where $R$ changes non-linearly (point-line parabolas and point-point bisectors) into short segments
and connect the introduced vertices to the two closest locations on the outline.
This allows us to directly generate accurate insets from the GMAT.

Note that by altering the outline by an infinitesimal change the straight skeleton of the polygon can be made to coincide with the GMAT.

We call any graph a GMAT if it contains the MAT and its segments are within the outline and the nodes have an accurate distance measure $R$ and the distance $R$ changes approximately linearly between two connected nodes.
The GMAT allows for extra segments.

We can generate an inset with rounded corners at distance $d$ by interpolating the $R$ at GMAT nodes and connecting the interpolated points.
Similarly one could compute an unmitered inset by connecting interpolated points along the straight skeleton.

\paragraph{Medial axis rather than Straight Skeleton}
See \cref{medial_axis_vs_straight_skeleton}.
Medial axis handles concave corners differently:
instead of generating the bisector, it will generate a parabolic arc in between the vertex and another line segment of the outline polygon.

@@

>>>>

\old{
\subsection{Method Overview}
\begin{enumerate}
\item compute medial axis transform (MAT)
\item find places `of high curvature' in the medial axis and mark those regions
\item transform the $R$ distance measures in the marked regions to enable fitting an integer multiple beads.
		This transformation uses transition regions to smoothly transition from $n$ into $n+1$ insets.
\item introduce extra `joints' on the medial axis in order to discretize the transformed distance measure
\item connect these new joints to the outline with new `bones' (In the standard MAT manner)
\item (optional) transform $R$ fields along all bones, while keeping the endpoint bead measures fixed. (Deviate from evenly distributed linear space in order to have outer outlines closer to the nominal bead width and only change the innermost couple of toolpaths.)
\item define locations everywhere on the bones of the medial axis at integer MAT distances
\item connect all locations with odd distance measure to form the inset toolpaths
\item connect all even locations to form the extent of the toolpaths, which defines the variable width of the segments.
\end{enumerate}
}

@@

Based on the straight skeleton naming, I would like to introduce a new consistent terminology:
\begin{itemize}
\item marked medial axis segment: vertebra
\item marked medial axis: spine
\item non-marked medial axis segment: arm
\item any medial axis segment: bone
\item bone introduced to the medial axis: rib
\item medial axis vert: joint
\item location of an insets along a bone: tick? locus?
\end{itemize}

@@

\subsubsection{Medial axis rather than Straight Skeleton}
See \cref{medial_axis_vs_straight_skeleton}.
Medial axis handles concave corners differently:
instead of generating the bisector, it will generate a parabolic arc in between the vertex and another line segment of the outline polygon.

@@

The bones of the medial axis which are not directly connected to the outline segment the area in as much sub-areas as the part has polygons.

\begin{figure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/MAT_example.pdf}
\caption{MAT}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/gMAT_example.pdf}
\caption{gMAT}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/gMAT_example_labeling.pdf}
\caption{Quads in gMAT}
\end{subfigure}
\caption{Grounded medial axis transform. Dark red are linear segments,  bright red are parabolic segments with high curvature, parabola segments with low curvature are purple. The labelings of areas show that the gMAT divides the area into quads and triangles and that the medial axis divides the area into sub-areas for each outline polygon.}
\label{gmat}
\end{figure}

\subsubsection{grounded Medial Axis Transform}
See \cref{gmat}.
The medial axis is commonly defined either as the set of points with more than one closest point on the boundary or as the set of quench sites of a fire started at the outline polygon growing inward.
A novel way of conceptualizing the medial axis is as a data structure which encodes the distance field.
The medial axis is the set of all points where the derivative of the distance field is discontinuous.

The medial axis transform (MAT) is the combination of the medial axis with at each node the distance values $R$.

We propose a modified MAT: the grounded medial axis transform: gMAT.
The distance field defined by the gMAT approximates the distance field of the MAT using \uwave{piece-wise linear quads}.
The gMAT is the set of all points where the derivative of the distance field is not constant.

Each node in the gMAT is connected to the outline via a \emph{single} bone.
This condition is violated on a MAT where there are concave outline verts.
The gMAT segments the polygon in quads consisting of 1 outline segment and 3 bones, one of which is not directly connected to the outline.
For concave verts the outline segments is missing and the quad becomes a triangle;
likewise for convex sections it may happen that the inner bone is missing from the quad so that it forms a triangle.

For a normal MAT it is already the case that
for a bone segment $v_0 v_1$ generated by two outline segments $p_0 p_1$ and $p_2 p_3$,
the distance on locations along $v_0 v_1$ can be interpolated linearly between $R(v_0)$ and $R(v_1)$.
The distance field between $v_0 v_1$ and $p_0 p_1$ can be constructed linearly as well.

For a MAT the same does not hold for parabolic bones or bones generated by two concave outline verts.
We therefore discretize these segments and connect the introduced nodes to the oulines using new ribs.
The resulting quads encode the original distance field in a piece-wise fashion using linear gradients.

The MAT is a subset of the Voronoi diagram inside the part, which in turn is a subset of the gMAT.
See \cref{voronoi_MAT}.

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{sources/method/voronoi_MAT.png}
\caption{From \citeauthor{lee1982medial} \cite{lee1982medial}}
\label{voronoi_MAT}
\end{figure}
